Assignment 5

### 2015-02-24 rmtw/a5/latex8.tex
Motivation added

The selection of development process, programming language and programming paradigm has a high impact on the development speed depending on what the the system requirements are and in which environment the system is developed. Selecting for example MDSD for the wrong system and setting may have a very negative impact on development speed, quality and maintainability. Since there seems to be a consensus in academia that MDSD is an improvement compared traditional software development \cite{staron2006adopting} \cite{volter2013model} and that most large software companies chose not to adopt MDSD, there is a need to methodically investigate the existing literature in which studies of the adoption of MDSD, and advantages and disadvantages of MDSD.

@@

*5 references only needed for above (re-use from a1)

Industry contradicts academia.

\Section{Purpose of the Study}
Purpose leading into RQs

>>>>

The selection of development process, programming language and programming paradigm has a high impact on the development speed depending on what the the system requirements are and in which environment the system is developed. Selecting for example MDSD for the wrong system and setting may have a very negative impact on development speed, quality and maintainability.

@@

Academia appears to be united in the opinion that MDSD is an improvement compared with traditional software development \cite{staron2006adopting} \cite{volter2013model}. However, why then do most large software companies chose not to adopt MDSD?

This gap in the literature is the motivation for our study. There is therefore a need to methodically investigate the existing literature in which studies of the adoption of MDSD, advantages and disadvantages of MDSD are explored. Not only this but how and when should MDSD be adopted and how it can be ensured to succeed.
